%\documentclass[a4]{article}

%\parindent0cm
%\parskip0.5cm

%\newenvironment{ex}[1]{
%\begin{quote}
%\underline{Example #1  :}}
%{\end{quote}}




%\begin{document}


%\begin{center}
%{\Large Worksheet 1.1: Order of Operations} \vspace{5mm}\\
%{\large Section 1} \\
%{\sc BIDMAS}
%\end{center}
%\hrule
%\vspace{5mm}

%\setcounter{section}{0}
%\subsection{Order of Operations}

%\subsubsection{BIDMAS}

\section{Order of Operations}

\subsection{BIDMAS}


When performing arithmetic operations 
 there is a particular order in which the
operations must be done.  If we fail to do things in the correct order,
we may end up with the wrong answer.  The order of operations is:-
\begin{enumerate}
\item
  Brackets
\item
  Indices
\item
  Division and multiplication
\item 
  Addition and subtraction
\end{enumerate}

Some people remember this as BIDMAS (an acronym for the above list).
This means that when looking at a calculation you should first do the
operations inside brackets, then do any division or multiplication,
working from left to right in the expression.
Finally do addition and subtraction, again working from left to right
in the expression.  
Powers should be treated as a
high-priority multiplication.


\begin{ex}{1}

What is $3 + 3\times 10$?

By BIDMAS we do the multiplication first, hence 
\begin{eqnarray*}
3 + 3\times 10 &=& 3+ 30\\
	       &=& 33
\end{eqnarray*}


\underline{Note:}  If we did not follow the correct order of 
operations we may have
got $60$ as our answer.
\end{ex}


	      


\begin{ex}{2}
What is $3 \times (7+2)+6$?
\begin{eqnarray*}
3 \times (7+2) +6 &=& 3 \times 9 +6 \quad \mbox{(do the bracket first)} \\
		  &=& 27+6 \quad \mbox{(then do the multiplication)} \\
		  &=&33
\end{eqnarray*}
\end{ex}
\begin{ex}{3}
What is    $3+15 \div (\frac{1}{2} \times 6)-9 \div 3^{2}$?
\begin{eqnarray*}
3+15 \div (\frac{1}{2} \times 6)-9 \div 3^{2} & = & 3+15 \div 3 - 9 \div 9  
\quad \mbox{(do brackets and indices first)} \\
				     &=& 3+5-1 
\quad \mbox{(then do division)} \\
				     &=& 7
\quad \mbox{(then work from left to right)} 
\end{eqnarray*}
\end{ex}
\begin{ex}{4}
 Work out $\frac{27}{3+6}$.

Note that $27$ must be divided by $(3+6)$, so we introduce brackets in
the expression.
\begin{eqnarray*}
\frac{27}{3+6} & = & 27 \div (3+6) \\
  & = & 27 \div 9 \\
 & = & 3
\end{eqnarray*}
If you try to do the calculation without the brackets on your
calculator, you will get an answer of $15$. Why?
\end{ex}


\subsubsection{}

\begin{enumerate}
\item Calculate the following, without the use of a calculator:
\begin{enumerate}
\item $3 + 4 \times 7$
\item $6 + (7 \times 3) - (6 + 4)$
\item $18 \div (4 + 2)$
\item $6 + 3^2 - 4 \times 2$
\item $\frac{48}{6+2}$
\item $12 - \frac{1}{2} \times 10 + 4^2 \div 2$
\end{enumerate}
\end{enumerate}

%\end{document}
