\documentclass[twoside=false,DIV=14]{scrartcl}

\input{../latex_setup.tex}
\title{\color{redish} \vspace{-1em}COMP2000 Week 1: Team Based Learning}

\begin{document}
{\color{blackish}\maketitle}\vspace{-7em}

\begin{abstract}
\end{abstract}

\section*{Topics}
\begin{description}
\item[What is TBL (TBL)]  
\item[Your rights and responsibilities (RAR)]  
\item[TBL Practice (PRT)]
\end{description}
\section*{Preparation}
\begin{itemize}
\item None this week, but in all future weeks you will need to \emph{pre-pepare} for class.  \emph{This week only} there will be a short explanation of TBL before we begin the class for real.  In future weeks \emph{there will be not lecture at the start of class}.  You will complete the RAT yourself, which is normally done \emph{before} class, then you will get into groups and complete the RAT again before we move on to the application exercise.
\end{itemize}


\newpage
\part*{RAT 1}
\section*{RAR: Basics of Team Work}
Which of the following (choose as many as apply) are vital for working in a team:
\begin{itemize}
    \item Respect of teammates
    \item Diligence to team work
    \item Being a reliable team member
    \item Clear communication between team members
    \item Inclusiveness
    \item Doing all the work yourself
\end{itemize}

\newpage
\part*{Application Exercise}
Your team has been assigned to develop a Team Based Learning worksheet for a topic of interest.  You should create a set of pre-readings (2 hours work), a RAT (20 minutes), and a set of application exercises (1 hour).  You should also create a set of answers for the RAT and application exercises.  You will be given 1 hour to work on this and then we will re-convene to discuss the various worksheets that were created.  Your group will be expected to share your worksheet with the class after 1 hour.  Your group can choose the topic of the worksheets from anything which is acceptable to \emph{polite society}\footnote{This means we avoid religion, politics and anything which could reasonably be thought to genuinely offend someone present.}
\newpage
\part*{Self Study Exercises}
None this week, but in future weeks there will be a set of exercsies, with solutions, for you to work on individually.  They will be great exam preparation.
\end{document}